Analysis

### 2022-01-26 docs/index.Rmd
ajustes R&R

---
author: " "
bibliography:
- 'input/bib/zlibrary.bib'
csl:
- 'input/bib/apa6.csl'
title: " "
output:
    bookdown::html_document2:
        smart: false
        includes:
          in_header: "input/head_github-activity.html"
---

@@

# This is the project website for the paper "Economic inequality and its influence on the justification of legitimate income differences. {.left}

>>>>

---
bibliography:
- '../input/bib/referencias.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    bookdown::html_document2:
        smart: false
        includes:
          in_header: "head_github-activity.html"
---

@@

# This is the project website for the paper "Economic inequality and its influence on the justification of legitimate income differences. {-}

### 2022-01-26 production/prod_analysis.rmd
ajustes R&R

```{r desc-treat, echo=TRUE, results='asis'}
pacman::p_load(dplyr,gtsummary,kableExtra,forcats)
table_format = if (knitr::is_html_output()) {
   #conditional instructions for kable
   "html" #if html set "html" in format
 } else if (knitr::is_latex_output()) {
   "latex"#if latex set "latex" in format
 }

>>>>

```{r desc-treat, echo=FALSE, results='asis'}
pacman::p_load(dplyr,gtsummary,kableExtra,forcats)
table_format = if (knitr::is_html_output()) {
   #conditional instructions for kable
   "html" #if html set "html" in format
 } else if (knitr::is_latex_output()) {
   "latex"#if latex set "latex" in format
 }
